---
title: "Penguins"
author: "Ahmed Muhumed"
date: "2022-12-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Penguins is a dataset comprising various measurements of three different penguin species, namely Adelie, Gentoo, and Chinstrap. Same as Iris data which had measurements of three different species of the Iris flower.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r}
library(ggplot2)
library(tidyverse)
library(dplyr)
library(palmerpenguins)
```


```{r}
# Assessing the dataset
head(penguins)
```

```{r}
#column names
colnames(penguins)
```

```{r}
# let us asses the structure of the dataset
str(penguins)
```

```{r}
#glimpse the dataset
glimpse(penguins)
```

```{r}
#count the penguin's species in the dataset
penguins %>%
  count(species)
```

```{r}
#summary of the dataset
summary(penguins)
```

```{r}
#looking for duplicated rows
n_distinct(penguins)
```

```{r}
# checking correlation between numeric variables
penguins %>% 
  drop_na() %>% 
  select_if(is.numeric) %>% 
  cor()
```

```{r}
ggplot(penguins) +
  geom_point(aes(flipper_length_mm, body_mass_g, color = species))
```

```{r}
ggplot(penguins) +
  geom_point(aes(bill_depth_mm, body_mass_g, color = species))
```

```{r}
ggplot(penguins) +
  geom_point(aes(bill_length_mm, body_mass_g, color = species))
```
```{r}
ggplot(penguins) +
  geom_density(aes(x = species, fill = species, alpha = 0.4))
```

```{r}
penguins_by_sex <- penguins %>% 
  filter(!is.na(sex)) %>% 
  group_by(species, sex) %>% 
  summarise(bill_depth_mm = mean(bill_depth_mm),
            bill_length_mm = mean(bill_length_mm),
            flipper_length_mm = mean(flipper_length_mm),
            body_mass_g = mean(body_mass_g))
```
```{r}
ggplot(penguins_by_sex, aes(x = species, y = flipper_length_mm, fill = sex)) +
  geom_col(position = position_dodge())
```





